SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-04-28 papers/B1555_EdgeOn/B1555_letter.tex
change in Table 2
new result of 2SIE w/ prior
Minor edit to figure captions

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
with contours from the MERLIN observation of \citet{Marlow99} overlaid. \textbf{From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).}
%
\label{fig:merlin}}
\end{figure}

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. From left to right, four components are A, B (merging doubles), D(lowest spot), and C(right).\label{fig2}}
\end{figure}

@@

$\sigma_1$ &$141.3$     & $144.9$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
\hline
$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
$y_2$	  &$-0.2502$	& $-0.1843$  \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.5$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
$\chi ^2$ & $1.05$ & $0.04$ \\
\hline
\end{tabular}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0481$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1620$    &  $+0.3682$ \\  
\hline
\end{tabular}

@@

\hline
	& MERLIN & VLA & \multicolumn{3}{l}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
$f_A/f_B$			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
$f_A/f_C$		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
$f_A/f_D$		&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\

@@

%\end{minipage}
\medskip
Comparison between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}. 1-SIE model is quoted from Table 5 in \citet{Marlow99}. [WE HAVE 1-SIE MODEL NOW. SHOULD I QUOTE FROM MARLOW OR OUR OWN?--JW]

>>>>

\begin{figure}
%\plotone{1555_ao_merlin_overlay.eps}
\includegraphics[width=84mm]{1555_ao_merlin_overlay.eps}
\caption{High-resolution  $K^\prime$ band imaging of the B1555+375 lens system 
with contours from the MERLIN observation of \citet{Marlow99} overlaid. 
%
\label{fig:merlin}}
\end{figure}

\begin{figure}
%\plotone{point_source.eps}
\includegraphics[width=84mm]{point_source.eps}
\caption{Radio observation(red open circle) and model-predicted(blue plus sign) image positions of B1555+375. The position of the source is at $(-0.2066,-0.1634)$ for SIE+Expdisk model, marked by a black filled circle. \label{fig2}}
\end{figure}

@@

$\sigma_1$ &$141.3$     & $144.9$ \\
$e_1$	  & $0.27$	& $0.27$ \\
$\theta_1$ &$105.5 \degr$ & $97.7 \degr$ \\
\hline
$x_2$	  &$-0.1615$ 	&$-0.1593$  \\
$y_2$	  &$-0.2502$	& $-0.1843$  \\
$M_{tot,2}$  & $3.59\times 10^{10} $  & ...	 \\  
$\sigma_2$ & ...        &$123.5$ \\  
$e_2$	  &$0.84$	&$0.83$  \\
$\theta_2$ &$7.4\degr$ &$7.4\degr$  \\
$r_e$	  & $0.20 ''$ &  ... \\
\hline
%$\chi ^2$ & $1.05$ & $0.04$ \\
%\hline
\end{tabular}

@@

Component	&\multicolumn{2}{c}{MERLIN} 	 & \multicolumn{4}{c}{Model} \\
					&\multicolumn{2}{c}{5 GHz}		&	\multicolumn{2}{c}{SIE+expdisk} &\multicolumn{2}{c}{ 2-SIE}		\\
					 &East &North &East 		&North &East 		&North\\ 
\hline
A ........ &$0$    		&$0$		&$0.0000$ &$0.0000$   &   $0.0000$   &  $ 0.0000$\\  
B ........ &$-0.0726$ 	&$+0.0480$	&$-0.0726$ &$+0.0479$ & $-0.0726 $  &  $+0.0480$  \\  
C ........ &$-0.4117$  &$-0.0280$	&$-0.4117$ &$-0.0280$  & $-0.4117 $  &   $+0.0280$ \\  
D ........ &$-0.1619$  &$-0.3680$	&$-0.1610$ &$-0.3678$  & $-0.1619$    &  $+0.3680$ \\  
\hline
\end{tabular}

@@

\hline
	& MERLIN & VLA & \multicolumn{3}{l}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
$f_A/f_B$			&$1.75$ & $1.78$ &$1.04$& $1.66$ & $1.75$ \\ 
$f_A/f_C$		&$2.05$ 	&$2.37$ &$3.20$ & $1.33$ & $2.27$\\
$f_A/f_D$		&$13.08$ &$ 12.86$ &$9.82$& $5.83$ & $8.11$\\

@@

%\end{minipage}
\medskip
Comparison between radio data and model-predicted flux ratios. The radio observation data is quoted from Tables 2 and Table 3 in \citet{Marlow99}.
